Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-12 papers/LREC2020/lrec2020naming.tex
updates acklowledgements

\section{Acknowledgments}
We thank the anonymous reviewers for their comments, and the AMT workers who participated in our crowdsourcing task.  
 This project has received funding from the European Research Council~(ERC) under the European Union's Horizon~2020 research and innovation programme (grant agreement No715154), from the Ramón y Cajal programme~(grant RYC-2015-18907), and by the Catalan government~(SGR 2017 1575).
 % Spanish  State  Research  Agency~(AEI) and  the  European  Regional  Development  Fund~(FEDER, UE) (project PGC2018-094029-A-I00). 
 This paper reflects the authors' view only,  and the EU is not responsible \mbox{for any use that may be made of the information it contains.}
 \hfill \includegraphics[scale=.03]{figures/LOGO_ERC-FLAG_EU_.jpg}
% Place all acknowledgements (including those concerning research grants and
% funding) in a separate section at the end of the article.

>>>>

\section{Acknowledgments}
We thank the anonymous reviewers for their comments, and the AMT workers who participated in our crowdsourcing task.  
 This project has received funding from the European Research Council~(ERC) under the European Union's Horizon~2020 research and innovation programme (grant agreement No715154) and by the Catalan government~(SGR 2017 1575).
 % Spanish  State  Research  Agency~(AEI) and  the  European  Regional  Development  Fund~(FEDER, UE) (project PGC2018-094029-A-I00). 
 This paper reflects the authors' view only,  and the EU is not responsible \mbox{for any use that may be made of the information it contains.}
 %\hfill \includegraphics[scale=.03]{figures/LOGO_ERC-FLAG_EU_.jpg}
 \begin{flushright}
 	\vspace{-2ex}
 	\includegraphics[scale=.03]{figures/LOGO_ERC-FLAG_EU_.jpg}
 \end{flushright}

% Place all acknowledgements (including those concerning research grants and
% funding) in a separate section at the end of the article.
